### 2019-04-24 pages/math/semi-comb/project/paper.tex
Update

\documentclass{amsart}
\usepackage[T1]{fontenc}
\usepackage{mathpazo}
%\usepackage[margin=1in]{geometry}
\usepackage[inline]{enumitem}
%\usepackage{rotating}
%\usepackage{color}
%\usepackage{tabu}
%\usepackage{parskip}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{calc}
\usepackage{xfrac}
\usepackage{mathtools}
\usepackage{cancel}
\usepackage{tikz}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{calc}
%\usepackage{xcolor-solarized}
%\usepackage{minted}
%\usepackage{MnSymbol}
%\usepackage[libertine]{newtxmath}
%\newcommand*\circled[1]{\tikz[baseline= (char.base)]{
    %\node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
%\usepackage{xypic}
%\usepackage[tightpage]{preview} % display
% Math operators
\DeclareMathOperator{\Z}{\mathbb{Z}}
\DeclareMathOperator{\Q}{\mathbb{Q}}
\DeclareMathOperator{\N}{\mathbb{N}}
\DeclareMathOperator{\R}{\mathbb{R}}
\DeclareMathOperator{\C}{\mathbb{C}}
\DeclareMathOperator{\F}{\mathbb{F}}
\DeclareMathOperator{\sge}{\mathsf{e}}
\DeclareMathOperator{\sgm}{\mathsf{m}}
\DeclareMathOperator{\sgG}{\mathsf{G}}
\DeclareMathOperator{\sgg}{\mathsf{g}}
\DeclareMathOperator{\sgF}{\mathsf{F}}
\DeclareMathOperator{\sgt}{\mathsf{t}}
\DeclareMathOperator{\sgL}{\mathsf{L}}
\DeclareMathOperator{\sgZ}{\mathsf{Z}}
\DeclareMathOperator{\sgAp}{Ap}
\DeclareMathOperator{\sgPF}{PF}
\DeclareMathOperator{\sgconv}{conv}
\DeclareMathOperator{\sgsupp}{supp}
\DeclareMathOperator{\calO}{\mathcal{O}}
\DeclareMathOperator{\Grho}{\prescript{}{\rho}G}
% Theorem environments
\theoremstyle{plain}
\newtheorem*{thm}{Theorem}
\newtheorem*{lemma}{Lemma}
\newtheorem*{claim}{Claim}
\newtheorem*{cor}{Corollary}
\newtheorem*{prop}{Proposition}
\newtheorem*{conj}{Conjecture}
\theoremstyle{remark}
\newtheorem*{example}{Example}
\theoremstyle{definition}
\newtheorem*{definition}{Definition}
% Paired math operators
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}
% Math helper functions
\newcommand{\congr}[2]{{[#1]}_{#2}}
\newcommand{\set}[1]{\{#1\}}
\newcommand{\genset}[1]{{\langle{}#1\rangle{}}}
\newcommand{\abs}[1]{\lvert{}#1\rvert{}}
\newcommand{\norm}[1]{\lVert{}#1\rVert{}}
\newcommand{\bmx}[1]{\begin{bmatrix}#1\end{bmatrix}}
\newcommand{\pmx}[1]{\begin{pmatrix}#1\end{pmatrix}}
  \newcommand{\sbmx}[1]{{\left[\begin{smallmatrix}#1\end{smallmatrix}\right]}}
\newcommand{\smallxymatrix}[2]{\xymatrix@C-=#1cm@R-=#1cm{#2}}
\renewcommand\labelitemi{\small$\bullet$}
\begin{document}
%
%
%
\noindent
\begin{quote}
  (13) \emph{Flow polytopes.}
  A \emph{directed graph} is a collection of dots (called \emph{vertices}) and
  arrow between them (called \emph{edges}). A \emph{flow} on a directed graph is a
  way to label each edge of $G$ by an element of $\Z$ (or $\Z_n$) so that at each
  vertex $v$, the sum of the edges entering $v$ equals the sum of the edges
  leaving $v$ (i.e.\ the in \emph{flow} at each vertex equals the \emph{out
  flow}). The flows on a given directed graph can be counted using a certain
  family of polytopes, whose integer points each coincide with a flow on $G$.
  \\[1em]
  \noindent
  Source:
  \emph{Combinatorial reciprocity theorems} (M. Beck, R. Sanyal), Chapters 1 and 7.
\end{quote}

@@

A graph $G=(V,E)$ is a collection of $V$ a set of vertices and $E$ a set of
edges between these vertices. Now, a graph doesn't have to have any vertices or
any edges (except that if it has edges there must be vertices to which those edges
connect).
Also note that the vertices of a graph can be elements of some arbitrary $\F^n$
space, but for this report we'll only concern ourselves with graphs in $\Z^2$
Euclidean space.

@@

  vertices are either directed connect via an edge or are connected to

@@

  \begin{tikzpicture}[every node/.style={draw,shape=circle,fill=white,inner sep=1}]

@@

  components which if removed would increase the number of connected

@@

So far we've only looked at graph which are \emph{unoriented}.

@@

  A \emph{directed} or \emph{oriented graph} is a graph is a graph on which we

@@

        every node/.style={draw,shape=circle,fill=white,inner sep=1},

@@

As an aside, directed graphs are the subject of many algorithms in computer
science, often pertaining to finding optimal ways to traverse the paths of said
graphs. In some models each edge is considered to be of equal ``weight'' as any
other. That is if two edges originating from the same node both point to the
same node, there should be no real preference to traveling down one edge or the
other to get to the destination. On the other hand we might assign a weight to
each edge, presenting a cost-benefit analysis in choosing a path to take (as in
figure~\ref{fig:path-finding} where the edge with weight 5 now becomes most
expensive to traverse versus the one with weight 2).
\begin{figure}[h]
  \begin{tikzpicture}[
    dot/.style={draw,shape=circle,fill=white,inner sep=1},
    decoration={markings,mark=at position 0.5 with {\arrow{>}}}
  ]
    \path (0,0) node[dot] (a){} (2,0) node[dot] (b){};
    \draw[postaction=decorate] (a) to [out=45, in=135] node[above]{} (b);
    \draw[postaction=decorate] (a) to [out=315,in=225] node[below]{$\phantom 5$} (b);
  \end{tikzpicture}
  \hspace{1cm}
  \begin{tikzpicture}[
    dot/.style={draw,shape=circle,fill=white,inner sep=1},
    decoration={markings,mark=at position 0.5 with {\arrow{>}}}
  ]
    \path (0,0) node[dot] (a){} (2,0) node[dot] (b){};
    \draw[postaction=decorate] (a) to [out=45, in=135] node[above]{$2$} (b);
    \draw[postaction=decorate] (a) to [out=315,in=225] node[below]{$5$} (b);
  \end{tikzpicture}
  \caption{A directed graph with and without weights.}
  \label{fig:path-finding}
\end{figure}

@@

>>>>

\documentclass{amsart}
\usepackage[T1]{fontenc}
\usepackage{mathpazo}
%\usepackage[margin=1in]{geometry}
\usepackage[inline]{enumitem}
%\usepackage{rotating}
%\usepackage{color}
%\usepackage{tabu}
%\usepackage{parskip}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{calc}
\usepackage{xfrac}
\usepackage{mathtools}
\usepackage{cancel}
\usepackage{tikz}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{calc}
%\usepackage{xcolor-solarized}
%\usepackage{minted}
%\usepackage{MnSymbol}
%\usepackage[libertine]{newtxmath}
%\newcommand*\circled[1]{\tikz[baseline= (char.base)]{
    %\node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
%\usepackage{xypic}
%\usepackage[tightpage]{preview} % display
% Math operators
\DeclareMathOperator{\Z}{\mathbb{Z}}
\DeclareMathOperator{\Q}{\mathbb{Q}}
\DeclareMathOperator{\N}{\mathbb{N}}
\DeclareMathOperator{\R}{\mathbb{R}}
\DeclareMathOperator{\C}{\mathbb{C}}
\DeclareMathOperator{\F}{\mathbb{F}}
\DeclareMathOperator{\sge}{\mathsf{e}}
\DeclareMathOperator{\sgm}{\mathsf{m}}
\DeclareMathOperator{\sgG}{\mathsf{G}}
\DeclareMathOperator{\sgg}{\mathsf{g}}
\DeclareMathOperator{\sgF}{\mathsf{F}}
\DeclareMathOperator{\sgt}{\mathsf{t}}
\DeclareMathOperator{\sgL}{\mathsf{L}}
\DeclareMathOperator{\sgZ}{\mathsf{Z}}
\DeclareMathOperator{\sgAp}{Ap}
\DeclareMathOperator{\sgPF}{PF}
\DeclareMathOperator{\sgconv}{conv}
\DeclareMathOperator{\sgsupp}{supp}
\DeclareMathOperator{\calO}{\mathcal{O}}
\DeclareMathOperator{\Grho}{\prescript{}{\rho}G}
% Theorem environments
\theoremstyle{plain}
\newtheorem*{thm}{Theorem}
\newtheorem*{lemma}{Lemma}
\newtheorem*{claim}{Claim}
\newtheorem*{cor}{Corollary}
\newtheorem*{prop}{Proposition}
\newtheorem*{conj}{Conjecture}
\theoremstyle{remark}
\newtheorem*{example}{Example}
\theoremstyle{definition}
\newtheorem*{definition}{Definition}
% Paired math operators
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}
% Math helper functions
\newcommand{\congr}[2]{{[#1]}_{#2}}
\newcommand{\set}[1]{\{#1\}}
\newcommand{\genset}[1]{{\langle{}#1\rangle{}}}
\newcommand{\abs}[1]{\lvert{}#1\rvert{}}
\newcommand{\norm}[1]{\lVert{}#1\rVert{}}
\newcommand{\bmx}[1]{\begin{bmatrix}#1\end{bmatrix}}
\newcommand{\pmx}[1]{\begin{pmatrix}#1\end{pmatrix}}
  \newcommand{\sbmx}[1]{{\left[\begin{smallmatrix}#1\end{smallmatrix}\right]}}
\newcommand{\smallxymatrix}[2]{\xymatrix@C-=#1cm@R-=#1cm{#2}}
\renewcommand\labelitemi{\small$\bullet$}
\begin{document}
%
%
%

\noindent
\begin{quote}
  (13) \emph{Flow polytopes.}
  A \emph{directed graph} is a collection of dots (called \emph{vertices}) and
  arrow between them (called \emph{edges}). A \emph{flow} on a directed graph is a
  way to label each edge of $G$ by an element of $\Z$ (or $\Z_n$) so that at each
  vertex $v$, the sum of the edges entering $v$ equals the sum of the edges
  leaving $v$ (i.e.\ the in \emph{flow} at each vertex equals the \emph{out
  flow}). The flows on a given directed graph can be counted using a certain
  family of polytopes, whose integer points each coincide with a flow on $G$.
  \\[1em]
  \noindent
  Source:
  \emph{Combinatorial reciprocity theorems} (M. Beck, R. Sanyal), Chapters 1 and 7.
\end{quote}

@@

A graph $G=(V,E)$ is a collection of $V$, a set of vertices, and $E$, a set of
edges between the vertices. Now, a graph doesn't have to have any vertices, nor
does it have to to have any edges (except that if it has edges there must be
vertices to which those edges connect).
Also note that the vertices of a graph can be elements of some arbitrary
d-dimensional space, but for this report we'll only concern ourselves with
graphs in some two-dimensional space.

@@

  vertices are either directly connected via an edge or are connected to

@@

  \begin{tikzpicture}[every node/.style={draw,shape=circle,fill=black,inner sep=1}]

@@

  components which, if removed, would increase the number of connected

@@

So far we've only looked at \emph{unoriented} graphs, but
now we introduce directions within graphs.

@@

  A \emph{directed} or \emph{oriented graph} is a graph on which we

@@

        every node/.style={draw,shape=circle,fill=black,inner sep=1},

@@

As an aside, directed graphs are the subject of many algorithms in computer
science, often pertaining to finding optimal ways to traverse the paths of said
graphs. In some models each edge is considered to be of equal ``weight'' as any
other. That is if two edges originating from the same node both point to the
same node, there should be no real preference to traveling down one edge or the
other to get to the destination. On the other hand we might assign a weight to
each edge, presenting a cost-benefit analysis in choosing a path to take (as in
figure~\ref{fig:path-finding} where the edge with weight 5 now becomes most
expensive to traverse versus the one with weight 2).
\begin{figure}[h]
  \begin{tikzpicture}[
    dot/.style={draw,shape=circle,fill=black,inner sep=1},
    decoration={markings,mark=at position 0.5 with {\arrow{>}}}
  ]
    \path (0,0) node[dot] (a){} (2,0) node[dot] (b){};
    \draw[postaction=decorate] (a) to [out=45, in=135] node[above]{} (b);
    \draw[postaction=decorate] (a) to [out=315,in=225] node[below]{$\phantom 5$} (b);
  \end{tikzpicture}
  \hspace{1cm}
  \begin{tikzpicture}[
    dot/.style={draw,shape=circle,fill=black,inner sep=1},
    decoration={markings,mark=at position 0.5 with {\arrow{>}}}
  ]
    \path (0,0) node[dot] (a){} (2,0) node[dot] (b){};
    \draw[postaction=decorate] (a) to [out=45, in=135] node[above]{$2$} (b);
    \draw[postaction=decorate] (a) to [out=315,in=225] node[below]{$5$} (b);
  \end{tikzpicture}
  \caption{A directed graph with and without weights.}
  \label{fig:path-finding}
\end{figure}

@@

\begin{figure}[h]
  \begin{subfigure}[t]{.3\textwidth}
    \begin{tikzpicture}[
        gdot/.style={draw,shape=circle,fill=black,inner sep=1},
        ddot/.style={draw,shape=circle,fill=white,inner sep=1},
        decoration={markings,mark=at position 0.5 with {\arrow{>}}}
      ]
      \draw (0,0) node[gdot](a){} -- (1,0) node[gdot](b){};
      \node[ddot](c) at (.5,-.5) {};
      \draw (c) to [out=180,in=90,looseness=60] (c);
    \end{tikzpicture}
    \caption{Simplest graph with a bridge.}
  \end{subfigure}
  \begin{subfigure}[t]{.3\textwidth}
    \begin{tikzpicture}[
        gdot/.style={draw,shape=circle,fill=black,inner sep=1},
        ddot/.style={draw,shape=circle,fill=white,inner sep=1},
        decoration={markings,mark=at position 0.5 with {\arrow{>}}}
      ]
      \draw (0,0) node[gdot]{} -- (1,0) node[gdot]{} -- ($(1/2,{sqrt(3)/2})$) node [gdot]{} -- cycle;
      \node[ddot] (a) at ($(1/2,{-sqrt(2)/3})$) {};
      \node[ddot] (b) at ($(1/2,{sqrt(3)/6})$) {};
      \draw (a) -- (b);
      \draw (a) to [out=180,in=135,looseness=4] (b);
      \draw (a) to [out=0,in=45,looseness=4] (b);
    \end{tikzpicture}
    \caption{A complete graph.}
  \end{subfigure}
  \begin{subfigure}[t]{.3\textwidth}
    \begin{tikzpicture}[
      gdot/.style={draw,shape=circle,fill=black,inner sep=1},
      ddot/.style={draw,shape=circle,fill=white,inner sep=1},
      decoration={markings,mark=at position 0.5 with {\arrow{>}}}
    ]
      \draw (0,0) node[gdot]{} -- (0,1) node[gdot]{};
      \draw (0,0) node[gdot]{} -- ($({sqrt(3)/2},1/2)$) node[gdot]{} -- (0,1) node[gdot]{} -- ($({-sqrt(3)/2},1/2)$) node[gdot]{} -- cycle;
      \node[ddot] (a) at (0,-1/2){};
      \node[ddot] (b) at ($({-sqrt(3)/6},1/2)$){};
      \node[ddot] (c) at ($({ sqrt(3)/6},1/2)$){};
      \draw (a) to [out=135,in=240] (b);
      \draw (a) to [out=180,in=120,looseness=4] (b);
      \draw (a) to [out=45,in=300] (c);
      \draw (a) to [out=0,in=60,looseness=4] (c);
      \draw (b) -- (c);
    \end{tikzpicture}
    \caption{Graph with two connected components.}
  \end{subfigure}
  \caption{Various graphs and their duals.}
  \label{fig:graphs-and-duals}
\end{figure}
